Title

### 2023-04-20 main.tex
last hope failed, maybe now

% }}}
\section{Pauli Channels}  \label{sec: Pauli Channels} % {{{
% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

@@

\cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
\cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
lo qeu se quiere decir en la seccion es otra cosa.}

@@

To describe open systems, instead of state vectors,
we use matrices $\rho$ that act on $\mathcal{H}$.
These matrices are called density matrices, and they include information about the system's interaction with its environment. 
For a density matrix $\rho$ to be physically valid, 
it must satisfy two conditions: $\tr(\rho) = 1$ and $\rho$ is positive semi-definite,
which is denoted as $\rho \geq 0$~\cite{chuangbook}.

Knowing this, we can now define quantum channels.
Quantum channels are operators $\mathcal{E}$ that
describe the evolution of open quantum systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.
Quantum channels are the most general linear operations
that a quantum system can undergo independently of its
past~\cite{zimansbook,cirac}.
These channels are constructed based on three fundamental properties: 
linearity, trace preservation, and complete positivity.

@@

% }}}
\subsection*{Pauli Channels} \label{subsec: Pauli Channels} % {{{

We have discussed the main features of quantum channels and 
now we turn our attention to a specific 
type of channel for $N$-qubit systems called Pauli channels.
First we will define these channels for single-qubit systems,
whose most general density matrix can be written as~\cite{chuangbook}:
\begin{equation}
\label{eq: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{equation}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
implies that the remaining $r_{1,2,3}$ form
a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere~\cite{Marinescu}.
That is, every possible density matrix for a one-qubit
system is uniquely associated with a point in a unit sphere. \cpnote{explicar un poco mejor. Me parece que para el publico vale 
la pena ser un poco mas explicito. pero no estoy muy seguro.}

Given a one-qubit system described by $\rho$, 
a Pauli channel is defined as an operation that with probability $k_{\gamma}$
applies the Pauli matrix $\sigma_{\gamma}$ to
the system, for $\gamma = 0,1,2,3$~\cite{geometry}.
Mathematically, the Pauli channel is written in the following way:
\begin{eqnarray}
\label{eq: Pauli channel 1 qbit}
\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
\end{eqnarray} 
where of course the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
have to be non-negative real numbers such that 
$\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
trace preserving and completely positive).

@@

\cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
se interpretara. Creo qe es mas que atenuacion de los componentes, o es solo atenuacion? 
en todo caso ver mejor como va la cosa. }

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting eq. (\ref{eq:  Density matrix Nqbit}) in eq. (\ref{eq: pauli channel N-qubit})
and using the property of eq. (\ref{eq: propiedad-pauli}):
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
\cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}

% }}}
\subsection*{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

@@

% }}}
% }}}

\newpage
\section*{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}

>>>>

% }}}
\section{Pauli Channels}  \label{sec: Pauli Channels} % {{{
\cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

@@

% \cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
% \cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
% lo qeu se quiere decir en la seccion es otra cosa.}

@@

To describe open systems, instead of state vectors,
we use matrices $\rho$ that act on $\mathcal{H}$.
These matrices are called density matrices, and they include information about the system's interaction with its environment. 
For a density matrix $\rho$ to be physically valid, 
it must satisfy two conditions: $\tr(\rho) = 1$ and it must be positive semi-definite,
which is denoted as $\rho \geq 0$~\cite{chuangbook}.

Knowing this, we can now define quantum channels.
Quantum channels are operators $\mathcal{E}$ that
can describe the evolution of open quantum systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.
Quantum channels are the most general linear operations
that a quantum system can undergo independently of its
past~\cite{zimansbook,cirac}.
These channels are constructed based on three fundamental properties: 
linearity, trace preservation, and complete positivity.

@@

\cpnote{Le hice un par de cambios pequeños pero la veo bastante bien. }
% }}}
\subsection*{Pauli Channels} \label{subsec: Pauli Channels} % {{{

We have discussed the main features of quantum channels and 
now we turn our attention to a specific 
type of channels for $N$-qubit systems called Pauli channels.
First we will define these channels for single-qubit systems,
whose most general density matrix can be written as~\cite{chuangbook}:
\begin{equation}
\label{eq: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{equation}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
implies that the remaining $r_{1,2,3}$ form
a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere~\cite{Marinescu}.
That is, every possible density matrix for a one-qubit
system is uniquely associated with a point in a unit sphere. 
% \cpnote{explicar un poco mejor. Me parece que para el publico vale 
% la pena ser un poco mas explicito. pero no estoy muy seguro.}

Given a one-qubit system described by $\rho$, 
a Pauli channel is defined as an operation that with probability $k_{\gamma}$
applies the Pauli matrix $\sigma_{\gamma}$ to
the system, for $\gamma = 0,1,2,3$~\cite{geometry}.
Mathematically, the Pauli channel is written in the following way:
\begin{eqnarray}
\label{eq: Pauli channel 1 qbit}
\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
\end{eqnarray} 
where the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
are non-negative real numbers such that 
$\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
trace preserving and completely positive).

@@

@@

As in the one qubit case, Pauli channels for $N$ qubits 
attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
This can be seen by substituting eq. (\ref{eq:  Density matrix Nqbit}) in eq. (\ref{eq: pauli channel N-qubit})
and using the property of eq. (\ref{eq: propiedad-pauli}):
\begin{align*}
\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
\end{align*}
which means that applying the Pauli channel multiplies the 
components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
% }}}
\subsection*{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

\cpnote{aca voy}

@@

% }}}
% }}}
\section*{OPR Circuits} % {{{
\label{sec: OPR Circuits}
Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
